{\sf NodIO}, a framework for evolutionary algorithms in JavaScript: first results

### 2016-01-06 special-issue-ci/volunteer-clouds-ieee-ci-si-tr.tex
Just a sentence

The need to use non-permanent and potentially massive computing
infrastructure for distributed scientific experiments has lead to the
rising of {\em volunteer computing} defined as a set of tools that allow
citizens to {\em donate} cycles to scientific experiments by running
an application \cite{Anderson06thecomputational}; this application can be embedded in a web page. And
since browsers are ubiquitous, these kind of systems are the ones that
we are interested the most and this has led us to create a framework for
evolutionary algorithm experiments that is able to work in that mode
\cite{DBLP:journals/corr/GuervosG15}. {\sf NodIO} is a
cloud or bare metal based volunteer evolutionary computing system
derived from the {\sf NodEO} library, whose architecture has been
developed using JavaScript on the client as well as the server.
All parts of the framework are free and available with a free license
from \url{https://github.com/JJ/splash-volunteer}.

>>>>

The need to use non-permanent and potentially massive computing
infrastructure for distributed scientific experiments has lead to the
rising of {\em volunteer computing} defined as a set of tools that allow
citizens to {\em donate} cycles to scientific experiments by running
an application \cite{Anderson06thecomputational}; this application can be embedded in a web page. And
since browsers are ubiquitous, we are more interested in these kind of systems, this has led us to create a framework for
evolutionary algorithm experiments that is able to work in that mode
\cite{DBLP:journals/corr/GuervosG15}. {\sf NodIO} is a
cloud or bare metal based volunteer evolutionary computing system
derived from the {\sf NodEO} library, whose architecture has been
developed using JavaScript on the client as well as the server.
All parts of the framework are free and available with a free license
from \url{https://github.com/JJ/splash-volunteer}.
